Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-09 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

%work in progress / noch nicht fertig
Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sicm+sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
  \caption{%
    \textbf{Two possible setups for a combined SIC and SSC microscope.}
    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sicm+sscm_setup}
\end{figure}

>>>>

%work in progress / noch nicht fertig
Scanning surface confocal microscopy (SSCM) \cite{Gorelik2002} is a combination of SICM and confocal 
microscopy tracking the sample surface. This combination enables simultaneous SICM and FM imaging of
the same region, in this case the surface, of the same sample at the same time. To achieve matching
field of views, pixel sizes and recording times consequentially yielding two correlating data sets,
two slightly different setups are imaginable and have been put to the test (see figure 
\ref{fig:sscm_setup}) \cite{Gorelik2002}\cite{Shevchuk2013}.
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sscm_setup}
  \caption{%
    \textbf{Two possible setups for a SSC microscope.}
    \textbf{a: Diagram of the combined setup with a xyz sample scan.}
    \textbf{b: Diagram of the combined setup with a xy sample scan and a z probe scan.} 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sicm+sscm_setup}
\end{figure}
The first setup (figure \ref{fig:sscm_setup}a), basically an inverted SIC microscope, holds the 
SICM probe at a fixed position. The focus of the confocal FM objective is adjusted to the tip of SICM 
probe for vertical alignment. To achieve lateral alignment of probe and pinhole mechanical 
micromanipulators are used. Once the setup is aligned, the sample stage moves the sample in all three 
dimensions (xyz) for imaging.
The second setup (figure \ref{fig:sscm_setup}b) is almost identical to the first with just one 
alteration: the sample stage only moves in xy dimensions while objective and probe have been equipped 
with an extra piezo element to enable movement in z direction. Thus, instead of moving the sample in
all three dimensions, it is only moved in x and y directions, while probe and objective simultaneously
move in z direction.
According to \cite{Shevchuk2013}, this change allows for faster scan rates as the resonant frequency
of the 3D piezo-actuator acted as a limiting factor. Additionally, usage of three piezo-elements on the
same platform lead to cross-talk and consequentially artefacts in the SICM data.
